---
title: "Basic usage of PGC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{basic_usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First we'll load up the package.

```{r setup}
library(pgc)
```

Now we need some example summary trial data. Let's generate some sequences of $T$ (time to completion for the trials), $N$, the number of centers, and $n$, the number of recruits per center

```{r}
# number of trials
samplesize = 50

N_seq = sapply(1:samplesize,function(i){
    x = rnbinom(1,mu=50,size=5)
    while(x<50)
        x = rnbinom(1,mu=50,size=5)
    return(x)
})
```

```{r}
n_seq = sapply(5*N_seq,function(m){
    x = rnbinom(1,mu=m,size=5)
    return(x)
})
```

```{r}
N_seq[N_seq==0] = 1
n_seq[n_seq==0] = 1

head(N_seq)
head(n_seq)
```

Now we'll generate the sequence of times given true values of $\alpha$ and $\beta$

```{r}
require('extraDistr')

true_alpha = 0.05
true_beta = 0.1

T_seq = sapply(1:samplesize,function(i)
            suppressWarnings({extraDistr::rbetapr(1,shape1=n_seq[i],shape2=true_alpha*N_seq[i],scale=true_beta)
    }))

head(T_seq)
```

We can estimate the MLEs for $\phi=\frac{\alpha}{\beta}$ and $\beta$ using `pgc`

```{r}
out = pgc::estimate(T_seq=T_seq,N_seq=N_seq,n_seq=n_seq)
```

and then look at the output

```{r}
out
```

We can see that these estimates are pretty close to our true values for $\phi$ and $\beta$.

```{r}
true_alpha/true_beta
true_beta
```
